---
title: "Accessing Twitter Data Using rtweet"
---


# Introduction

This file uses contains code to access Tweets from the Twitter API. Much of the initial code was taken from this excellent lab (https://mkearney.github.io/nicar_tworkshop/#1), created by the mkearney - the developer of rtweet.



# Library necessary packages
```{r}
library(rtweet)
library(tidyverse)
library(tidytext)
library(textdata)
library(dplyr)
library(stringr)
library(tidyr)
library(lubridate)
library(ggplot2)
library(RColorBrewer)
library(gridExtra)
library(sentimentr)
```



# Set rootpath
```{r}
# Set rootpath to wherever you have cloned the GitHub repository to
rp <- "C:/Users/sgmmahon/Documents/GitHub/iom_project/"

# Define path to accessing_tweets directory
at <- "methods/accessing_tweets/"
```



# Create Twitter token
```{r}
# Create token
token <- create_token(
  app = "GDS Analysis",
  consumer_key = "38Vl2dWJnq9f1E4IwxCP8KayZ",
  consumer_secret = "pUmwnjjxo7Gnfe8nMyBXuIUy4U8GH0EuvRIkdnd8nyk6fCpmch",
  access_token = "1065962179806052352-f8B4U1JWaAM6h6uIe5PnrvPHaCVu29",
  access_secret = "dZzhsfM1up9uoR7WB6CKAXK8NS3WXoDUjaCGd9Kvf99EL",
  set_renv = FALSE )

# Save token
path_to_token <- paste0(rp,at,"twitter_token.rds")
saveRDS(token, path_to_token)

# Create env variable TWITTER_PAT (with path to saved token)
env_var <- paste0("TWITTER_PAT=", path_to_token)

# Save as .Renviron file (or append if the file already exists)
cat(env_var, file = paste0(rp,at,".Renviron"), fill = TRUE)

# Refresh .Renviron variables
readRenviron(paste0(rp,at,".Renviron"))
```




# Define geographies for 5 countries within study

rtweet uses a function call lookup_coords() to obtain the geographies of specific regions. This function relies on the Google Geocoding API. Given that Google charges for use of its API and this study only requires 5 geographies, I decided to simply use define these regions manually based on the outputs from a single call of the API. These are defined below.
```{r}
# Define function which creates geographies that mimic rtweet's lookup_coords() output
assign_coords <- function(x) {
  coords <- list(place = x[[1]],
                 box = x[[2]],
                 point = x[[3]])
  names(coords$box)   <- c("sw.lng", "sw.lat", "ne.lng", "ne.lat")
  names(coords$point) <- c("lat", "lng")
  class(coords)       <- c("coords", "list")
  return(coords)
}

# Define input features for function
ukvars    <- list("UK",c(-8.89890, 34.56140, 33.91655, 60.91570),c(55.378051, -3.435973))
usavars   <- list("usa",c(-124.84897, 24.39631, -66.88544, 49.38436),c(36.890, -95.867))
spainvars <- list("spain",c(-18.2648, 27.4985, 4.6362, 43.8504),c(40.46367, -3.74922))
italyvars <- list("italy",c(6.62672, 35.48970, 18.79760, 47.09200),c(41.87194, 12.56738))
grmanvars <- list("germany",c(5.866343, 47.270111, 15.041896, 55.081500),c(51.16569, 10.45153))

# Create geographies
uk_coords    <- assign_coords(ukvars)
usa_coords   <- assign_coords(usavars)
spain_coords <- assign_coords(spainvars)
italy_coords <- assign_coords(italyvars)
grman_coords <- assign_coords(grmanvars)

# View results
#uk_coords
```



# Define search terms
```{r}
search_terms_en <- list(
  
  # Migrant terms
  neutral_migrant_terms_1 = c("immigrant", "immigration", "migrant", "migration", "\"asylum seeker\"", "refugee", "\"undocumented worker\""), 
  neutral_migrant_terms_2 = c("\"guest worker\"", "\"EU worker\"", "\"non-UK workers\"", "\"foreign worker\"", "(human smuggling)", 
                              "(human trafficking)"),
  negative_migrant_terms  = c("illegals", "foreigner", "\"illegal alien\"", "\"illegal worker\""),
  
  # Racial terms
  #neutral_racial_terms    = c("china", "chinese", "Asian", "\"china town\"", "chinatown", "japan", "Japanese", "korea", "Korean", "Africa", "African",
  #                           "Vietnam", "Vietnamese", "muslim", "islam", "ethnic", "gypsy", "polish", "poles", "Romanian"),
  
  negative_racial_terms   = c("islamophob", "sinophob", "\"china flu\"", "\"kung flu\"", "\"china virus\"", "\"chinese virus\"", "shangainese"),
  
  # Twitter accounts
  pro_migrant_account_1   = c("@UNmigration", "@IOM_UN", "@IOMatUN", "@IOMatEU", "@IOM_UK", "@IOMResearch", "@IOM_GMDAC", "@hrw", "@Right_to_Remain"),
  pro_migrant_account_2   = c("@CommonsHomeAffs", "@fcukba", "@Mark_George_QC", "@MigrantVoiceUK", "@MigrantChildren", "@MigrantHelp", "@thevoiceofdws"),
  pro_migrant_account_3   = c("@WORCrights", "@UbuntuGlasgow", "@MigrantsUnionUK", "@migrants_rights", "@MigrantsMRC", "@Consenant_UK", "@RomaSupport"),
  pro_migrant_account_4   = c("@MigrantsLawProj", "@MigRightsScot", "@IRMOLondon", "@HighlySkilledUK", "@WeBelong19", "@Project17UK"),
  neutral_account         = c("@ukhomeoffice", "@pritipatel", "@UKHomeSecretary", "@EUHomeAffairs", "@MigrMatters", "@MigObs"),
  anti_migrant_account    = c("@Nigel_Farage", "@MigrationWatch"),
  
  # Hashtags
  positive_hashtags       = c("#RefugeesWelcome", "#MigrantsWelcome", "#LeaveNoOneBehind", "#FreedomForImmigrants", "#illegalmigantsUK", "#LondonIsOpen",
                              "#EndHostileEnvironment", "#FamiliesBelongTogether"),
  neutral_hashtags        = c("#Pritiuseless", "#migrationEU", "#immigration", "#migration", "#immigrant", "#migrant", "#immigrate", "#migrate", "#refugees",
                             "#NigelFarage", "#ImmigrationReform"),
  negative_hashtags_1     = c("#illegals", "#foreigner", "#foreigners", "#illegalalien", "#illegalaliens", "#illegalworker", "#OurCountry", "#illegalworkers"),
  negative_hashtags_2     = c("#KeepThemOut", "#SendThemBack", "#migrantsnotwelcome", "#refugeesnotwelcome", "#illegals", "#ChinaVirus", "#chinaflu"),
  negative_hashtags_3     = c("#kungflu", "#chinesevirus", "#TheyHaveToGoBack", "#DeportThemAll"),
  event_hashtags          = c("#Moria", "#CampFire", "#closethecamps")
  
)

search_terms_it <- list(
  
  # Migrant terms
  italy_neutral_migrant_terms  = c("Immigrat", "richiedent", "asilo", "person", "irregolar", "migrant", "stranier", "rifugiat", "cittadinanza", "nazionalità", 
                                  "\"vittima di tratta\"", "\"minore non accompagnato\"", "\"traffico di migranti\"", "sbarco", "sbarchi"),
  italy_negative_migrant_terms = c("Clandestin", "illegal", "profug", "immigrat", "abusiv", "invasione"),
  
  # Racial terms
  #italy_neutral_racial_terms   = c("\"Persona di colore\"", "\"Persone di colore\"", "afrodiscendent", "person", "near", "african", "oriental", "marocchin",
  #                                 "Senegales", "tunisin", "cines", "asiatic", "nigerian", "rom", "arab", "magrebin", "razzismo", "discriminazione"),
  italy_negative_racial_terms  = c("zingar", "negr", "sporco", "sporch", "scimmi", "zingar", "extracomunitari"),
  
  # Twitter accounts
  italy_pro_migrant_account_1  = c("@UNmigration", "@IOM_UN", "@IOMatUN", "@IOMatEU", "@IOMResearch", "@OIMItalia", "@IOM_GMDAC", "@LHartIOM", "@hrw",
                                   "@Refugees", "@MSF_Sea", "@RefugeesIntl", "@DetentionForum", "@OpenSociety", "@Amnesty", "@FilippoGrandi", "@IOMchief",
                                   "@UNSR_Migration", "@PICUM_post", "@seawatch_intl"),
  italy_pro_migrant_account_2  = c("@emergency_ong", "@amnestyitalia", "@SeaWatchItaly", "@BaobabExp", "@aboubakar_soum", "@CaritasItaliana", "@cartadiroma",
                                   "@caritas_milano", "@open_migration", "@Medhope_FCEI", "@MSF_ITALIA", "@OIMItalia", "@UNHCRItalia", "@SOSMedItalia"),
  italy_pro_migrant_account_3  = c("@openarms_it", "@RescueMed", "@UNICEF_Italia", "@valigiablu", "@OxfamItalia", "@CIRRIFUGIATI", "@SaveChildrenIT",
                                   "@InMigrazione", "@Pontifex", "@CentroAstalli"),
  italy_neutral_account        = c("@Viminale", "@EUHomeAffairs", "@GiuseppeConteIT", "@ItalyMFA"),
  italy_anti_migrant_account   = c("@matteosalvinimi", "@giorgiameloni", "@CasaPoundItalia", "@ForzaNuova", "@FratellidItalia", "@LegaSalvini", "@Dsantanche",
                                   "@ilgiornale", "@Libero_official", "@lumorisi", "@RobertoFioreFN"),
  italy_positive_hashtags_1    = c("#portiaperti", "#apriamoiporti", "#aprireiporti", "#accoglienza", "#bastarazzismo", "#fatelientrare", "#SeaWatch",
                                   "#SeaEye", "#Openarms", "#TuttiFratelli", "#3ottobre"), 
  italy_positive_hashtags_1    = c("#restiamoumani", "#regolarizzazione", "#corridoiumanitari", "#solidarieta", "#dirittodiasilo", "#ioaccolgo"),
  italy_neutral_hashtags       = c("#DecretiSicurezza", "#decretoimmigrazione", "#migranti", "#migrazioni", "#immigrati", "#immigrazione", "#SAR",
                                   "#searchandrescue", "#stranieri", "#richiedentiasilo", "#asilo", "#rifugiati", "#integrazione", "#ONG", "#iussoli",
                                   "#decretiSalvini", "#razzismo", "#cittadinanza", "#MareNostrum", "#reinsediamento", "#rimpatri", "#Mediterraneo",
                                   "#RegolamentoDublino", "#hotspot", "#tratta"),
  italy_negative_hashtags      = c("#portichiusi", "#tolleranzazero", "#descretisicurezza", "#decretosalvini", "#decretoimmigrazione", "#BloccoNavale",
                                   "#blocconavalesubito", "#chiudiamoiporti", "#invasione", "#lamorgesedimettiti", "#extracomunitari", "#clandestini",
                                   "#profughi", "#irregolari", "#ItaliaAgliItaliani", "#aiutiamoliacasaloro", "#primagliitaliani", "#Decretoclandestini",
                                   "#DifendiamolItalia", "#iostoconSalvini"),
  italy_event_hashtags         = c("#Moria", "#Etienne", "#Abou", "#Lesbo", "#WillyMonteroDuarte", "#WillyMonteiro")

)

# Country Search Terms
uk_add_terms     = ' (place_country:GB OR profile_country:GB) '
usa_add_terms    = ' (place_country:US OR profile_country:US) '
spain_add_terms  = ' (place_country:ES OR profile_country:ES) '
italy_add_terms  = ' (place_country:IT OR profile_country:IT) '
grman_add_terms  = ' (place_country:DE OR profile_country:DE) '
```

# Access tweets
```{r}
# Function which concatonates search terms into a single string
stcat <- function(x) {
  paste0("(", paste(x, collapse = " OR "), ")")
}

# Function which searches for tweets in a specified geography, in a specified language, that are not retweets
tweet_search_criteria <- function(x,y,z) {
  twts <- search_tweets(q = stcat(x), lang = y, geocode = z,
                        include_rts = FALSE, n = 18000, retryonratelimit = TRUE)
}

# Search for tweets
#tweets_list <- list()
#for (i in 1:length(search_terms)) {
#  tweets_list[[i]] <- tweet_search_criteria(search_terms[[i]], "en", uk_coords)
#  cat("\r",i," of ",length(search_terms)," complete.")
#}
```


```{r}
# Save tweets
#saveRDS(tweets_list, paste0(rp, "data/tweet_data/tweets/7_day_sample_04102020_13102020.RData"))
```

```{r}
# Read in tweets
tweets_list <- readRDS(paste0(rp, "data/tweet_data/tweets/7_day_sample_04102020_13102020.RData"))
```

# Format tweets
```{r}
# Clean tweets
tweets <- tweets_list %>% 
  # rbind different all dataframes together
  do.call(rbind, .) %>%
  # Keep only unique cases
  distinct(status_id, .keep_all = TRUE) %>%
  # Order tweets by date-time
  .[order(.$created_at, decreasing = TRUE),] %>%
  # Convert text to lowercase
  mutate(full_text_cleaned = text %>% str_to_lower) %>%
  # Remove unwanted characters
  mutate(full_text_cleaned = full_text_cleaned %>% str_remove_all(pattern = '\\n')) %>% 
  mutate(full_text_cleaned = full_text_cleaned %>% str_remove_all(pattern = '&amp')) %>% 
  # Remove websites
  mutate(full_text_cleaned = full_text_cleaned %>% str_remove_all(pattern = 'https://t.co/[a-z,A-Z,0-9]*')) %>% 
  mutate(full_text_cleaned = full_text_cleaned %>% str_remove_all(pattern = 'http://t.co/[a-z,A-Z,0-9]*')) %>% 
  mutate(full_text_cleaned = full_text_cleaned %>% str_remove_all(pattern = 'https')) %>% 
  mutate(full_text_cleaned = full_text_cleaned %>% str_remove_all(pattern = 'http')) %>% 
  # Remove hashtags
  mutate(full_text_cleaned = full_text_cleaned %>% str_remove_all(pattern = '#')) %>% 
  # Remove entire hashtags (optional)
  # mutate(full_text_cleaned = full_text_cleaned %>% str_remove_all(pattern = '#[a-z,A-Z]*')) %>% 
  # Remove accounts
  mutate(full_text_cleaned = full_text_cleaned %>% str_remove_all(pattern = '@[a-z,A-Z]*')) %>% 
  # Remove retweet text
  mutate(full_text_cleaned = full_text_cleaned %>% str_remove_all(pattern = 'rt [a-z,A-Z]*: ')) %>% 
  mutate(full_text_cleaned = full_text_cleaned %>% str_remove(pattern = '^(rt)')) %>% 
  mutate(full_text_cleaned = full_text_cleaned %>% str_remove_all(pattern = '\\_')) %>%
  mutate(full_text_cleaned = full_text_cleaned %>% str_remove_all(pattern = 'ht [a-z,A-Z]*: ')) %>% 
  mutate(full_text_cleaned = full_text_cleaned %>% str_remove(pattern = '^(ht)'))


# Create POSICxt variable at the day level
tweets$day  <- format(tweets$created_at, "%Y-%m-%d")

# Create date-time variable at the hour level
tweets$hour_dt <- format(tweets$created_at, "%Y-%m-%d %H")

# Create numeric variable at the hour level
tweets$hour_t <- format(tweets$created_at, "%H") %>% as.numeric()

# Subset tweets to only include those on days where all hours are present
tweets <- subset(tweets, tweets$day != "2020-10-13" & tweets$day != "2020-10-04" )
```


# Plot hourly tweets
```{r}
# Split tweets by hour
tweets_hsplt <- split(tweets, tweets$hour_dt)

# lapply function which get the number of tweets within each split dataframe
tweets_hrntw <- lapply(tweets_hsplt, function(x) x <- nrow(x))

# Plot hourly tweets
plot(unlist(tweets_hrntw), type = "l", lty = 1)
```

# Sentiment Analysis
```{r}
extract_sentiments_coreNLP <- function(a) {
  a$index <- 1:nrow(a) %/% 100
  
  no_tweets <- a %>% split(.$day) %>%
    lapply(function(x) nrow(x) )
  
  whole_day <- a %>% 
    split(.$day) %>%
    lapply(function(x) split(x, x$index) ) %>%
    lapply(function(x) lapply(x, function(y) get_sentences(as.character(y[,"full_text_cleaned"])) %>% sentiment() ) ) %>%
    lapply(function(x) do.call(rbind, x) ) %>%
    lapply(function(x) sum(x$sentiment)) %>%
    mapply(function(x,y) x/y, ., no_tweets)
  
  midday <- a %>% 
    subset(.$hour_t <= 13) %>% 
    split(.$day) %>%
    lapply(function(x) x[1:1500,]) %>%
    lapply(function(x) split(x, x$index) ) %>%
    lapply(function(x) lapply(x, function(y) get_sentences(as.character(y[,"full_text_cleaned"])) %>% sentiment() ) ) %>%
    lapply(function(x) do.call(rbind, x) ) %>%
    lapply(function(x) sum(x$sentiment)) %>%
    lapply(function(x) x/1500 )
    
  
  max_activity <- a %>% split(.$day) %>%
    lapply(function(x) split(x, x$hour_dt) ) %>%
    lapply(function(x) lapply(x, function(y) nrow(y) ) ) %>%
    lapply(function(x) which.max(x) )
  
  max_hour <- a %>% split(.$day)
  for (i in 1:length(max_hour)) {
    max_hour[[i]] <- subset(max_hour[[i]], max_hour[[i]]$hour_t <= (max_activity[[i]]+1) )
  }
  max_hour <- lapply(max_hour, function(x) x[1:1500,]) %>%
    lapply(function(x) split(x, x$index) ) %>%
    lapply(function(x) lapply(x, function(y) get_sentences(as.character(y[,"full_text_cleaned"])) %>% sentiment() ) ) %>%
    lapply(function(x) do.call(rbind, x) ) %>%
    lapply(function(x) sum(x$sentiment)) %>%
    lapply(function(x) x/1500 )
  
  sentiments <- data.frame(whole_day = unlist(whole_day),
                           midday    = unlist(midday),
                           max_hour  = unlist(max_hour)
                           )
  return(sentiments)
}

# Function which calculates the sentiment of each tweet using 
# any of the tidytext libraries: nrc, afinn, bing
tidy_tweets <- function(x,y) {
  ttws <- x[,c("status_id","full_text_cleaned")] %>%
    unnest_tokens(word, full_text_cleaned) %>%
    inner_join(get_sentiments(y))
  if (y == "nrc" | y == "bing") {
    ttws <- ttws %>% filter(sentiment %in% c("positive","negative")) %>%
      count(status_id, sentiment) %>%
      spread(sentiment, n, fill = 0) %>%
      mutate(sentiment = positive - negative)
  } else {
    ttws <- ttws %>% group_by(status_id) %>%
      summarise(sentiment = sum(value))
  }
  ttws <- merge(tweets[,c("status_id","day","hour_t")], ttws, by = "status_id")
  return(ttws)
}

extract_sentiments <- function(a,b) {
  tidy_tweets <- tidy_tweets(a,b)
  
  no_tweets <- a %>% split(.$day) %>%
    lapply(function(x) nrow(x) )
  
  whole_day <- a %>% 
    split(.$day) %>%
    lapply(function(x) tidy_tweets[(tidy_tweets$status_id %in% x$status_id),]) %>%
    lapply(function(x) sum(x$sentiment)) %>%
    mapply(function(x,y) x/y, ., no_tweets)
  
  midday <- a %>% 
    subset(.$hour_t <= 13) %>% 
    split(.$day) %>%
    lapply(function(x) x[1:1500,]) %>%
    lapply(function(x) tidy_tweets[(tidy_tweets$status_id %in% x$status_id),]) %>%
    lapply(function(x) sum(x$sentiment)) %>%
    lapply(function(x) x/1500 )
    
  
  max_activity <- a %>% split(.$day) %>%
    lapply(function(x) split(x, x$hour_dt) ) %>%
    lapply(function(x) lapply(x, function(y) nrow(y) ) ) %>%
    lapply(function(x) which.max(x) )
  
  max_hour <- a %>% split(.$day)
  for (i in 1:length(max_hour)) {
    max_hour[[i]] <- subset(max_hour[[i]], max_hour[[i]]$hour_t <= (max_activity[[i]]+1) )
  }
  max_hour <- lapply(max_hour, function(x) x[1:1500,]) %>%
    lapply(function(x) tidy_tweets[(tidy_tweets$status_id %in% x$status_id),]) %>%
    lapply(function(x) sum(x$sentiment)) %>%
    lapply(function(x) x/1500 )
  
  sentiments <- data.frame(whole_day = unlist(whole_day),
                           midday    = unlist(midday),
                           max_hour  = unlist(max_hour)
                           )
  return(sentiments)
}

tidy_tweets_nrc <- function(x,y) {
  ttws <- x[,c("status_id","full_text_cleaned")] %>%
    unnest_tokens(word, full_text_cleaned) %>%
    inner_join(get_sentiments("nrc")) %>% 
    filter(sentiment %in% y) %>%
    count(status_id, sentiment) %>%
    spread(sentiment, n, fill = 0) %>%
    merge(tweets[,c("status_id","day","hour_t")], ., by = "status_id")
  names(ttws) <- c("status_id", "day", "hour_t", "sentiment")
  return(ttws)
}

extract_nrc_emotions <- function(a,b) {
  tidy_tweets <- tidy_tweets_nrc(a,b)
  
  no_tweets <- a %>% split(.$day) %>%
    lapply(function(x) nrow(x) )
  
  whole_day <- a %>% 
    split(.$day) %>%
    lapply(function(x) tidy_tweets[(tidy_tweets$status_id %in% x$status_id),]) %>%
    lapply(function(x) sum(x$sentiment)) %>%
    mapply(function(x,y) x/y, ., no_tweets)

  midday <- a %>% 
    subset(.$hour_t <= 13) %>% 
    split(.$day) %>%
    lapply(function(x) x[1:1500,]) %>%
    lapply(function(x) tidy_tweets[(tidy_tweets$status_id %in% x$status_id),]) %>%
    lapply(function(x) sum(x$sentiment)) %>%
    lapply(function(x) x/1500 )
    
  
  max_activity <- a %>% split(.$day) %>%
    lapply(function(x) split(x, x$hour_dt) ) %>%
    lapply(function(x) lapply(x, function(y) nrow(y) ) ) %>%
    lapply(function(x) which.max(x) )
  
  max_hour <- a %>% split(.$day)
  for (i in 1:length(max_hour)) {
    max_hour[[i]] <- subset(max_hour[[i]], max_hour[[i]]$hour_t <= (max_activity[[i]]+1) )
  }
  max_hour <- lapply(max_hour, function(x) x[1:1500,]) %>%
    lapply(function(x) tidy_tweets[(tidy_tweets$status_id %in% x$status_id),]) %>%
    lapply(function(x) sum(x$sentiment)) %>%
    lapply(function(x) x/1500 )
  
  sentiments <- data.frame(whole_day = unlist(whole_day),
                           midday    = unlist(midday),
                           max_hour  = unlist(max_hour)
                           )
  return(sentiments)
}

plot_graph <- function(x,y) {
  graph_data <- x %>% mutate(day = rownames(.)) %>%
    gather(method, sentiment, whole_day:max_hour, factor_key = TRUE) %>%
    .[order(.$day),] %>% arrange()
  
  graph <- ggplot(graph_data, aes(x = day, y = sentiment, fill = method)) +
    geom_bar(stat='identity', position=position_dodge()) +
    theme_light() + 
    ggtitle(paste0(y, " Sentiment Comparison")) +
    theme(plot.title = element_text(hjust=0.5)) +
    scale_fill_manual(name="Method", labels=c("Whole Day", "Midday", "Max Hour"), values=c("#737373", "#78C679", "#3690C0")) +
    xlab("") +
    theme(axis.text.x = element_text(angle = 30, hjust = 1)) +
    ylab("Sentiment")
  return(graph)
}
```



```{r}
coreNLP_sentiments <- extract_sentiments_coreNLP(tweets)
afinn_sentiments   <- extract_sentiments(tweets, "afinn")
bing_sentiments    <- extract_sentiments(tweets, "bing")
nrc_sentiments     <- extract_sentiments(tweets, "nrc")
nrc_anger          <- extract_nrc_emotions(tweets, "anger")
nrc_anticipation   <- extract_nrc_emotions(tweets, "anticipation")
nrc_disgust        <- extract_nrc_emotions(tweets, "disgust")
nrc_fear           <- extract_nrc_emotions(tweets, "fear")
nrc_joy            <- extract_nrc_emotions(tweets, "joy")
nrc_sadness        <- extract_nrc_emotions(tweets, "sadness")
nrc_surprise       <- extract_nrc_emotions(tweets, "surprise")
nrc_trust          <- extract_nrc_emotions(tweets, "trust")
```

```{r, fig.width=14, fig.length=20}
nlp          <- plot_graph(coreNLP_sentiments, "coreNLP")
afinn        <- plot_graph(afinn_sentiments, "AFINN")
bing         <- plot_graph(bing_sentiments, "Bing")
nrc          <- plot_graph(nrc_sentiments, "NRC")
anger        <- plot_graph(nrc_anger, "NRC Anger")
anticipation <- plot_graph(nrc_anticipation, "NRC Anticipation")
disgust      <- plot_graph(nrc_disgust, "NRC Disgust")
fear         <- plot_graph(nrc_fear, "NRC Fear")
joy          <- plot_graph(nrc_joy, "NRC Joy")
sadness      <- plot_graph(nrc_anticipation, "NRC Sadness")
surprise     <- plot_graph(nrc_anticipation, "NRC Surprise")
trust        <- plot_graph(nrc_anticipation, "NRC Trust")

grid.arrange(nlp, afinn, bing, 
             nrc, anger, anticipation, 
             disgust, fear, joy, 
             sadness, surprise, trust, ncol = 3)
```

```{r, fig.width=14, fig.length=20}
png(file= paste0(rp,"fig/sentiment_lexicons_test.png"), units="px", width=4000, height=2800, res=300)
grid.arrange(nlp, afinn, bing, 
             nrc, anger, anticipation, 
             disgust, fear, joy, 
             sadness, surprise, trust, ncol = 3)
dev.off()
```



```{r}
sentiment_correlation <- data.frame(
  
  emotion  = c("NLP", "AFINN", "Bing", "NRC", "NRC Anger", "NRC Anticipation", "NRC Disgust", 
               "NRC Fear", "NRC Joy", "NRC Sadness", "NRC Surprise", "NRC Trust"),
  
  midday   = c(stats::cor(coreNLP_sentiments$whole_day,coreNLP_sentiments$midday, method = "spearman"),
               stats::cor(afinn_sentiments$whole_day,afinn_sentiments$midday, method = "spearman"),
               stats::cor(bing_sentiments$whole_day,bing_sentiments$midday, method = "spearman"),
               stats::cor(nrc_sentiments$whole_day,nrc_sentiments$midday, method = "spearman"),
               stats::cor(nrc_anger$whole_day,nrc_anger$midday, method = "spearman"),
               stats::cor(nrc_anticipation$whole_day,nrc_anticipation$midday, method = "spearman"),
               stats::cor(nrc_disgust$whole_day,nrc_disgust$midday, method = "spearman"),
               stats::cor(nrc_fear$whole_day,nrc_fear$midday, method = "spearman"),
               stats::cor(nrc_joy$whole_day,nrc_joy$midday, method = "spearman"),
               stats::cor(nrc_sadness$whole_day,nrc_sadness$midday, method = "spearman"),
               stats::cor(nrc_surprise$whole_day,nrc_surprise$midday, method = "spearman"),
               stats::cor(nrc_trust$whole_day,nrc_trust$midday, method = "spearman") ),
  
  max_hour = c(stats::cor(coreNLP_sentiments$whole_day,coreNLP_sentiments$max_hour, method = "spearman"),
               stats::cor(afinn_sentiments$whole_day,afinn_sentiments$max_hour, method = "spearman"),
               stats::cor(bing_sentiments$whole_day,bing_sentiments$max_hour, method = "spearman"),
               stats::cor(nrc_sentiments$whole_day,nrc_sentiments$max_hour, method = "spearman"),
               stats::cor(nrc_anger$whole_day,nrc_anger$max_hour, method = "spearman"),
               stats::cor(nrc_anticipation$whole_day,nrc_anticipation$max_hour, method = "spearman"),
               stats::cor(nrc_disgust$whole_day,nrc_disgust$max_hour, method = "spearman"),
               stats::cor(nrc_fear$whole_day,nrc_fear$max_hour, method = "spearman"),
               stats::cor(nrc_joy$whole_day,nrc_joy$max_hour, method = "spearman"),
               stats::cor(nrc_sadness$whole_day,nrc_sadness$max_hour, method = "spearman"),
               stats::cor(nrc_surprise$whole_day,nrc_surprise$max_hour, method = "spearman"),
               stats::cor(nrc_trust$whole_day,nrc_trust$max_hour, method = "spearman") ) 
)

sentiment_correlation
```



```{r, fig.width=14}
graph_data <- sentiment_correlation %>% gather(method, correlation, midday:max_hour, factor_key = TRUE) %>%
  .[order(.$emotion),] %>% arrange()

sentiment_lexicons_corr <- ggplot(graph_data, aes(x = emotion, y = correlation, fill = method)) +
  geom_bar(stat='identity', position=position_dodge()) +
  theme_light() + 
  ggtitle("Comparison of Midday & Max-Hour\nSamples to Whole Day Sentiment") +
  theme(plot.title = element_text(hjust=0.5)) +
  scale_fill_manual(name="Method", labels=c("Midday", "Max Hour"), values=c("#78C679", "#3690C0")) +
  scale_y_continuous(limits = c(-1, 1)) +
  xlab("") +
  ylab("Correlation with Whole Day Sentiment")
sentiment_lexicons_corr
```

```{r, fig.width=14, fig.length=20}
png(file= paste0(rp,"fig/sentiment_lexicons_correlation.png"), units="px", width=4000, height=2800, res=300)
sentiment_lexicons_corr
dev.off()
```




















## Code for selecting colour pallettes
```{r}
# Hexadecimal color specification 
brewer.pal(n = 8, name = "Greys")
```

```{r}
# View a single RColorBrewer palette by specifying its name
display.brewer.pal(n = 8, name = 'Greys')
```

```{r, fig.height=7}
display.brewer.all()
```



